---
title: "BabyView Function Word Extraction"
output: html_document
---

```{r setup, include=FALSE}
library(readr)
library(dplyr)
library(stringr)
library(tidyr)
library(arrow)
```

# Loading BabyView Data

## Early Data (younger children)

```{r load_early}
early_transcripts <- read_csv("early_data/babyview-transcripts-2025.2.csv")
early_metadata    <- read_csv("early_data/babyview-metadata-2025.2.csv")
early_demographics <- read_csv("early_data/babyview-demographics-2025.2.csv")

# Strip BOM from any column names
names(early_metadata)     <- str_remove_all(names(early_metadata),     "﻿")
names(early_demographics) <- str_remove_all(names(early_demographics), "﻿")
```

```{r merge_early}
# Extract the unique_video_id embedded at the end of each video_id
# Format: {subject_id}_{date}_{num}_{unique_video_id}
early_transcripts <- early_transcripts %>%
  mutate(unique_video_id = str_extract(video_id, "[^_]+$"))

# Join metadata (age, subject_id) and demographics
early_data <- early_transcripts %>%
  left_join(
    early_metadata %>% select(unique_video_id, subject_id, `age (years)`),
    by = "unique_video_id"
  ) %>%
  left_join(
    early_demographics %>% select(subject_id, hispanic, ethnicity, sex),
    by = "subject_id"
  ) %>%
  rename(
    gloss     = token,
    age_years = `age (years)`
  ) %>%
  mutate(source = "early")
```
```{r}
glimpse(early_data)
```

## Later Data (older children)

```{r load_later}
later_transcripts <- read_csv("later_data/token_transcripts.csv")
```

```{r prep_later}
later_data <- later_transcripts %>%
  rename(
    gloss      = token,
    subject_id = pid,
    age_years  = age
  ) %>%
  rename_with(~ if_else(.x == "gender", "sex", .x)) %>%
  mutate(source = "later")
```

```{r}
glimpse(later_data)
```
## Combining into One Dataset

```{r combine}
# Select common columns before combining; keep demographics for potential analysis
babyview_tokens <- bind_rows(
  early_data %>% select(gloss, speaker, age_years, subject_id,
                        hispanic, ethnicity, sex, source) %>%
    mutate(hispanic = as.character(hispanic)),
  later_data %>% select(gloss, speaker, age_years, subject_id,
                        hispanic, ethnicity, sex, source) %>%
    mutate(hispanic = as.character(hispanic))
)
```

# Token Processing

## Lowercase

```{r lowercase}
babyview_tokens$gloss <- tolower(babyview_tokens$gloss)
```

## Exclusions

```{r exclusions}
n_tokens_before <- nrow(babyview_tokens)

# Remove rows without age information
babyview_tokens <- babyview_tokens %>% drop_na(age_years)

n_after_age_na <- nrow(babyview_tokens)

# Age cap: keep children under 6 years (72 months), consistent with CHILDES processing
babyview_tokens <- babyview_tokens %>% filter(age_years < 6)

n_after_age_cap <- nrow(babyview_tokens)

exclusions <- data.frame(
  n_before           = n_tokens_before,
  n_after_age_na     = n_after_age_na,
  n_after_age_cap    = n_after_age_cap,
  removed_age_na     = n_tokens_before   - n_after_age_na,
  removed_age_cap    = n_after_age_na    - n_after_age_cap
)

write_csv(exclusions, "../raw_data/babyview_exclusions_summary.csv")
```

## Coding Speaker Roles

```{r speaker_roles}
# Early: KCHI = key child, OCH = other child, FEM/MAL/unknown = adult
# Later: kchild = key child, ochild = other child, radult/tadult = adult
babyview_tokens <- babyview_tokens %>%
  mutate(speaker = case_when(
    speaker %in% c("KCHI", "kchild") ~ "child",
    speaker %in% c("OCH",  "ochild") ~ "other_child",
    speaker %in% c("FEM", "MAL", "radult", "tadult") ~ "parent",
    TRUE ~ "unknown"
  ))
```

## Coding Age

```{r age}
# Convert age from years to months and bin by floor, matching CHILDES `age` column
babyview_tokens <- babyview_tokens %>%
  mutate(
    target_child_age = age_years * 12,
    age = floor(target_child_age)
  )
```

# Contractions

Separate contracted morphemes so they can be counted as distinct functional morphemes,
mirroring the approach in `processing/functionword_extraction.Rmd`.

```{r contractions_prep}
babyview_tokens_contract <- babyview_tokens %>%
  mutate(gloss = str_replace(gloss, "cannot", "cann'ot")) %>%
  mutate(gloss = str_replace(gloss, "can't",  "cann't")) %>%
  mutate(gloss = str_replace(gloss, "won't",  "wont"))
```

```{r contractions_split}
contract_pattern <- "n't|'ll|'s|'d|'m|'re|n'ot|'ve"

# Rows containing a contraction
contractions <- babyview_tokens_contract %>%
  filter(str_detect(gloss, contract_pattern))

# Rows without any contraction
babyview_tokens_contract <- babyview_tokens_contract %>%
  filter(!str_detect(gloss, contract_pattern))

# Split contracted rows into stem row and suffix row
contracted <- contractions %>%
  mutate(gloss = str_remove_all(gloss, contract_pattern))

suffixes <- contractions %>%
  mutate(gloss = str_extract(gloss, contract_pattern))

# Reassemble
babyview_tokens_contract <- bind_rows(
  babyview_tokens_contract,
  contracted,
  suffixes
) %>%
  mutate(
    gloss = str_replace(gloss, "n'ot", "not"),
    gloss = str_replace(gloss, "wont", "won't")
  )
```

# Defining Function Words

## Non-contracted version

```{r function_words}
babyview_tokens$word <- "nonfunction"

function_words <- c(
  "no", "not", "I'm", "you're", "he's", "she's", "it's", "we're", "they're",
  "i've", "you've", "we've", "they've", "i'd", "you'd", "he'd", "she'd", "we'd",
  "they'd", "i'll", "you'll", "he'll", "she'll", "we'll", "they'll",
  "don't", "doesn't", "didn't", "isn't", "aren't", "wasn't", "weren't",
  "haven't", "hasn't", "hadn't", "can't", "couldn't", "won't", "wouldn't", "shouldn't",
  "yes", "and", "or", "if", "nor", "therefore",
  "none", "some", "each", "every", "all", "most", "few", "many", "several",
  "both", "everyone", "someone", "somebody", "everybody", "nonone",
  "everything", "something", "nowhere", "somewhere", "everywhere",
  "more", "less", "much", "least", "than",
  "one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten",
  "first", "second", "third", "fourth", "fifth", "sixth", "seventh", "eighth",
  "nineth", "tenth", "last",
  "can", "could", "need", "may", "might", "should", "ought", "must",
  "maybe", "perhaps", "shall", "will", "would", "won't",
  "any", "anyone", "anything", "anywhere", "anyway", "anyways", "ever", "yet",
  "the", "a", "an",
  "this", "that", "these", "those",
  "always", "usually", "seldom", "never", "sometimes", "often", "once", "twice", "now",
  "while", "after", "before", "then", "until", "since", "whenever", "during",
  "who", "when", "what", "whose", "where", "how", "why", "whom",
  "on", "in", "out", "up", "down", "under", "above", "below", "along", "over",
  "behind", "across", "beside", "between", "beyond", "into", "near", "onto",
  "toward", "here", "through", "there",
  "because", "but", "although",
  "am", "is", "are", "was", "were", "be", "been", "being",
  "have", "has", "had", "having", "do", "does", "did", "doing",
  "i", "you", "we", "he", "she", "they", "me", "us", "her", "him", "them",
  "my", "your", "our", "his", "their", "its",
  "mine", "yours", "ours", "hers", "theirs",
  "myself", "yourself", "ourselves", "himself", "herself", "yourselves", "themselves",
  "it", "itself",
  "again", "too", "also", "another", "other", "others", "still",
  "only", "just", "even", "indeed",
  "either", "neither", "whether", "as", "else", "almost", "already",
  "except", "for", "from", "instead", "such", "with", "without",
  "about", "by", "very", "unless", "to", "of", "at", "against",
  "outside", "inside", "so"
)

for (x in function_words) {
  babyview_tokens$word[babyview_tokens$gloss == x] <- x
}
```

## Contracted version

```{r function_words_contract}
babyview_tokens_contract$word <- "nonfunction"

function_words_contract <- c(
  "no", "not", "n't", "'ll", "'s", "'d", "'m", "'re", "'ve",
  "yes", "and", "or", "if", "nor", "therefore",
  "none", "some", "each", "every", "all", "most", "few", "many", "several",
  "both", "everyone", "someone", "somebody", "everybody", "nonone",
  "everything", "something", "nowhere", "somewhere", "everywhere",
  "more", "less", "much", "least", "than",
  "one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten",
  "first", "second", "third", "fourth", "fifth", "sixth", "seventh", "eighth",
  "nineth", "tenth", "last",
  "can", "could", "need", "may", "might", "should", "ought", "must",
  "maybe", "perhaps", "shall", "will", "would", "won't",
  "any", "anyone", "anything", "anywhere", "anyway", "anyways", "ever", "yet",
  "the", "a", "an",
  "this", "that", "these", "those",
  "always", "usually", "seldom", "never", "sometimes", "often", "once", "twice", "now",
  "while", "after", "before", "then", "until", "since", "whenever", "during",
  "who", "when", "what", "whose", "where", "how", "why", "whom",
  "on", "in", "out", "up", "down", "under", "above", "below", "along", "over",
  "behind", "across", "beside", "between", "beyond", "into", "near", "onto",
  "toward", "here", "through", "there",
  "because", "but", "although",
  "am", "is", "are", "was", "were", "be", "been", "being",
  "have", "has", "had", "having", "do", "does", "did", "doing",
  "i", "you", "we", "he", "she", "they", "me", "us", "her", "him", "them",
  "my", "your", "our", "his", "their", "its",
  "mine", "yours", "ours", "hers", "theirs",
  "myself", "yourself", "ourselves", "himself", "herself", "yourselves", "themselves",
  "it", "itself",
  "again", "too", "also", "another", "other", "others", "still",
  "only", "just", "even", "indeed",
  "either", "neither", "whether", "as", "else", "almost", "already",
  "except", "for", "from", "instead", "such", "with", "without",
  "about", "by", "very", "unless", "to", "of", "at", "against",
  "outside", "inside", "so"
)

for (x in function_words_contract) {
  babyview_tokens_contract$word[babyview_tokens_contract$gloss == x] <- x
}
```

# Word Categories

```{r word_categories}
label_categories <- function(df) {
  df$word_category <- "nonfunction"

  logical_connectives  <- c("no", "not", "and", "or", "if", "nor", "therefore")
  quantifiers          <- c("none", "some", "each", "every", "all", "most", "few", "many",
                            "several", "both", "everyone", "someone", "somebody", "everybody",
                            "nonone", "everything", "something", "nowhere", "somewhere", "everywhere")
  quantity             <- c("more", "less", "much", "most", "least", "than")
  cardinals            <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine", "ten")
  ordinals             <- c("first", "second", "third", "fourth", "fifth", "sixth", "seventh",
                            "eighth", "nineth", "tenth", "last")
  modals               <- c("can", "could", "need", "may", "might", "should", "ought", "must",
                            "maybe", "perhaps", "shall", "will", "would", "won't")
  NPI                  <- c("any", "anyone", "anything", "anywhere", "anyway", "anyways", "ever", "yet")
  definites            <- c("the", "a", "an")
  demonstratives       <- c("this", "that", "these", "those")
  temporal_quantifiers <- c("always", "usually", "seldom", "never", "sometimes", "often",
                            "once", "twice", "now")
  temporal_connectives <- c("while", "after", "before", "then", "until", "since", "whenever", "during")
  Wh                   <- c("who", "when", "what", "whose", "where", "how", "why", "whom")
  locatives            <- c("on", "in", "out", "up", "down", "under", "above", "below", "along",
                            "over", "behind", "across", "beside", "between", "beyond", "into",
                            "near", "onto", "toward", "here", "through", "there")
  causatives           <- c("because")
  contrasts            <- c("but", "although")
  auxiliaries          <- c("am", "is", "are", "was", "were", "be", "been", "being",
                            "have", "has", "had", "having", "do", "does", "did", "doing")
  pronouns             <- c("i", "you", "we", "he", "she", "they", "me", "us", "her", "him", "them",
                            "my", "your", "our", "his", "their", "its",
                            "mine", "yours", "ours", "hers", "theirs",
                            "myself", "yourself", "ourselves", "himself", "herself",
                            "yourselves", "themselves", "it", "itself")
  additives            <- c("again", "too", "also", "another", "other", "others", "still")
  exclusives           <- c("only", "just")
  focus                <- c("even", "indeed")
  other                <- c("either", "neither", "whether", "as", "else", "almost", "already",
                            "except", "for", "from", "instead", "such", "with", "without",
                            "about", "by", "very", "unless", "to", "of", "at", "against")

  categories <- list(
    "Logicals"            = logical_connectives,
    "Quantifiers"         = quantifiers,
    "Quantity"            = quantity,
    "Cardinals"           = cardinals,
    "Ordinals"            = ordinals,
    "Modals"              = modals,
    "NPI"                 = NPI,
    "Definites"           = definites,
    "Demonstratives"      = demonstratives,
    "Temporal Quantifiers"= temporal_quantifiers,
    "Temporal Connectives"= temporal_connectives,
    "Wh"                  = Wh,
    "Locatives"           = locatives,
    "Causal Connectives"  = causatives,
    "Contrast Connectives"= contrasts,
    "auxiliaries"         = auxiliaries,
    "Pronouns"            = pronouns,
    "Additives"           = additives,
    "Exclusives"          = exclusives,
    "Focus Particles"     = focus,
    "Other"               = other
  )

  for (cat in names(categories)) {
    df$word_category[df$gloss %in% categories[[cat]]] <- cat
  }

  df
}
```

```{r apply_categories}
babyview_tokens          <- label_categories(babyview_tokens)
babyview_tokens_contract <- label_categories(babyview_tokens_contract)
```

## Contracted version: also label n't and clitic suffixes

```{r contract_logicals}
babyview_tokens_contract$word_category[babyview_tokens_contract$gloss == "n't"] <- "Logicals"
```

# Syntactic Category

```{r syncategory}
babyview_tokens$syncategory <- "Function"
babyview_tokens$syncategory[babyview_tokens$word_category == "nonfunction"] <- "nonfunction"

babyview_tokens_contract$syncategory <- "Function"
babyview_tokens_contract$syncategory[babyview_tokens_contract$word_category == "nonfunction"] <- "nonfunction"
```

# Saving Output

```{r save}
write_feather(babyview_tokens,          "../processed_data/babyview_tokens_processed.feather")
write_feather(babyview_tokens_contract, "../processed_data/babyview_tokens_contract_processed.feather")
```
